---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LRpadding

<!-- badges: start -->
<!-- badges: end -->

LRpadding is a very short term project to implement a simple padding functionality for logistic regression,
 allowing the concatenation of arbitrarily many zeros on both the predictors and 
the response.  This is part of a much larger project, this code is entirely for testing and development.

Without an intercept, padding in this way would result in no effect (simply multiplying the likelihood by a constant),
so we assume we include an intercept as the first column of the model matrix.

## Installation

You can install the current version of LRpadding from GitHub with:

``` 
remotes::install_github('CCGill/LRpadding')
```
We make use of the excellent RcppNumerical package (http://cran.r-project.org/package=RcppNumerical),
and a simple example version of the RcppNumerical function fastLR, which is built on the L-BFGS 
algorithm for unconstrained minimization problems based on the LBFGS++ library.


## Example

This is a basic example problem demonstrating that a logistic_reg implementation on padded response/model 
agrees with the implementation of the padding.  It is based on a unit test for this package.  Note 
that the logistic_reg function is currently identical to the example version of fastLR from the RcppNumerical package.

We also show that our results closely matches the corresponding glm call.

```{r example}
library(LRpadding)
## basic example code
set.seed(42)
    
    n = 20000
    p = 100L
    x = matrix(rnorm(n * p), n)
    x = cbind(rep(1,n),scale(x,scale = F,center = T)) ##attach the intercept
    beta = runif(p+1)
    xbeta = c(x %*% beta)
    probs = 1 / (1 + exp(-xbeta))
    y = rbinom(n, 1, probs)
    testpadding = 40000L
  
    padded_x <- rbind(x,t(matrix( rep.int(c(1,0), c(1,p)), p+1, testpadding)))
    padded_y <- c(y,rep(0,testpadding))
    
    res1 <- logistic_reg(padded_x, padded_y) 
    res2 <- padded_logistic_reg(x,y,padding = testpadding)
    
    max(abs(res1 - res2)) ## identical results


```

A second example, for time.

```{r example 2,warning = F,message = F}
    set.seed(42)
    system.time(res1 <- logistic_reg(padded_x, padded_y) )
 
    system.time(res2 <- padded_logistic_reg(x,y,padding = testpadding))

    system.time(res3 <- glm.fit(padded_x,padded_y,family = binomial())$coefficients)

    max(abs(res1 - res2)) ## identical results

    max(abs(res2 - res3))
    
```
